### 2020-09-17 priority-gv.tex
Minor changes.

\subsection{Typing}
\input{fig/pgv-typing}
See \cref{fig:pgv-typing}.

\subsection{Operational Semantics}
\input{fig/pgv-operational-semantics}
See \cref{fig:pgv-operational-semantics}.

@@

\begin{corollary}[Closed Progress, $\cred$]
  \label{thm:pgv-closed-progress-confs}
  If $\cseq[\phi]{\ty{\Gamma}}{\conf{C}}$, then either:
  \begin{description}[labelwidth=8ex]
  \item[Done]
    There exists some $\tm{V}$ such that $\tm{\conf{C}}=\tm{\phi\;V}$;
  \item[Step]
    There exists some $\tm{\conf{D}}$ such that $\tm{\conf{C}} \cred \tm{\conf{D}}$; or
  \end{description}
\end{corollary}

>>>>

\subsection{Typing}
See \cref{fig:pgv-typing}.
\input{fig/pgv-typing}

\subsection{Operational Semantics}
See \cref{fig:pgv-operational-semantics}.
\input{fig/pgv-operational-semantics}

@@

\begin{corollary}[Closed Progress, $\cred$]
  \label{thm:pgv-closed-progress-confs}
  If $\cseq[\phi]{\emptyenv}{\conf{C}}$, then either:
  \begin{description}[labelwidth=8ex]
  \item[Done]
    There exists some $\tm{V}$ such that $\tm{\conf{C}}=\tm{\phi\;V}$; or
  \item[Step]
    There exists some $\tm{\conf{D}}$ such that $\tm{\conf{C}} \cred \tm{\conf{D}}$.
  \end{description}
\end{corollary}
